---
title: "Debug Article Titles"
author: "Ian and Chris"
date: "02/23/2022"
output:
  html_document:
    toc: yes
    toc_depth: 5
  pdf_document:
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_depth: 5
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir="../products") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_chunk$set(cache = TRUE)

library(tm)
library(stm)

source("../R/utils/coauthorship-graph-helper-functions.R")
```

## Introduction

Chris identified some articles that needed to appear in our 1990s Author+Article+Community graph in order for it to be considered valid.
This document represents Ian's work to track down the articles - and this was successful.

The ultimate purpose of this work is to ensure that our topic modelling can proceed with a sufficient number of titles per community.
Having tracked down the missing articles, I think this is now possible.

## Setting up the graphs

### Journal Graph

The Journal Graph consists of all the articles published in journals in the 1990s, along with the authors who published those articles.
The authors are connected to the journals via "authorship" edges.
The authors alre also connected to one-another via "coauthorship" edges.

Here we load the graph and display some summary/diagnostic information about it.

```{r load_journal_graph}
journal_graph = read.graph("../data/graphs/journals-1990s.graphml", format = "graphml")
journal_graph
```

We can visualize the Journal Graph to see that we have loaded something that looks like the network we expected.
There are lots of nodes, they have the names of authors and articles, and there are connections among them.

```{r plot_journal_graph}
plot(journal_graph, layout=layout_with_lgl, vertex.size=1, vertex.label.cex=0.2)
```

### Main Component of Graph

The main component graph contains all of the authors and articles who have some collaboration link among them.
This step also identifies communities using louvain clustering.
Clustering was applied to a graph containing both articles and authors so that articles will tend to be assigned membership according to the relative contributions of all co-authors.

```{r load_main_component_graph}
main_component_graph = get_main_component(journal_graph)
main_component_graph
```

```{r plot_main_component_graph}
plot(main_component_graph, layout=layout_with_lgl, vertex.size=1, vertex.label.cex=0.2)
```

We can inspect these graphs to verify that certain authors are present:

```{r test_find_author}
find_author(journal_graph, "Pennebaker, James W.")
find_author(main_component_graph, "Pennebaker, James W.")
```

### Article Communities

The resulting data frame contains the articles, along with community membership, for the main component.

```{r get_article_communities}
df_article_communities = get.data.frame(main_component_graph, what="vertices")
df_article_communities = df_article_communities[df_article_communities$node_type=="article",]
df_article_communities = df_article_communities[c("doi", "title", "issn", "abstract", "membership")]
df_article_communities$title = tolower(df_article_communities$title)

head(df_article_communities, n=1)
nrow(df_article_communities)
```

## Testing for presence of expected articles

Once we've applied our planned the filters and transforms, we inspect the resulting data frame to ensure that certain articles are still present.

### Finding an article we expected

The article **Stereotype threat effects on black and white athletic performance** does appear in the communities DF, demonstrating that the code works.

```{r check_article_communities_1}
sum(df_article_communities$title == "linguistic styles: language use as an individual difference")
```

The article is in the journal_graph too.

```{r check_journal_graph_1}
V(journal_graph)[V(journal_graph)$title == "Linguistic styles: Language use as an individual difference"]
```

### One articles that does not appear in DF

An article not present in the journal_graph looks like this:

```{r check_journal_graph_not_found}
V(journal_graph)[V(journal_graph)$node_type == "article" & V(journal_graph)$title == "tHis aRtiCLe doEs NoT ExISt"]
```

The article **Construction of Circumplex Scales for the Inventory of Interpersonal Problems** is present in the journal_graph.

```{r check_journal_graph_2}
V(journal_graph)[V(journal_graph)$node_type == "article" & V(journal_graph)$title == "Construction of Circumplex Scales for the Inventory of Interpersonal Problems"]
```

We can look at the communities df.  It is also present in our final data frame.

```{r check_article_communities_2}
sum(df_article_communities$title == "construction of circumplex scales for the inventory of interpersonal problems")
```

### Other articles that are expected in the data frame

Quite a few articles were missing - but these are all now in the data frame.

```{r others_not_found}
sum(df_article_communities$title == "construction of circumplex scales for the inventory of interpersonal problems")
sum(df_article_communities$title == "personality trait structure as a human universal")
sum(df_article_communities$title == "evaluating stability and change in personality and depression")
sum(df_article_communities$title == "on the accuracy of personality judgment: a realistic approach")
sum(df_article_communities$title == "the divided self: concurrent and longitudinal effects of psychological adjustment and social roles on self-concept differentiation")
```
