---
title: "Debug Article Titles"
author: "Ian Dennis Miller"
date: "10/25/2021"
output:
  html_document:
    toc: yes
    toc_depth: 5
  pdf_document:
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_depth: 5
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir="../products") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tm)
library(stm)

source("../R/utils/coauthorship-graph-helper-functions.R")
```

## Setting up the graph

```{r}
co_authorship_graph = read.graph("../data/graphs/coauthors-merged-journals-1990s.graphml", format = "graphml")
co_authorship_graph
```


```{r}
journal_graph = read.graph("../data/graphs/journals-1990s.graphml", format = "graphml")
journal_graph
```

### Main Component

```{r}
main_component_graph = get_main_component(co_authorship_graph)
main_component_graph
```

### Article Communities

```{r}
df_article_communities = get_article_communities(journal_graph, main_component_graph)
head(df_article_communities)
```

## Testing for presence of expected articles

### Finding an article we expected

This article does appear in the DF and demonstrates that the code works 

```{r}
sum(df_article_communities$title == "Authoritarianism of Parents and Offspring: Intergenerational Politics and Adjustment to College")
# V(main_component_graph)[V(main_component_graph)$title == "Authoritarianism of Parents and Offspring: Intergenerational Politics and Adjustment to College"]
```

### Articles that do not appear in DF

The following article is present in the journal_graph but not the article_communities.

```{r}
V(journal_graph)[V(journal_graph)$node_type == "article" & V(journal_graph)$title == "Authoritarianism of Parents and Offspring: Intergenerational Politics and Adjustment to College"]
```

```{r}
V(journal_graph)[V(journal_graph)$node_type == "article" & V(journal_graph)$title == "Construction of Circumplex Scales for the Inventory of Interpersonal Problems"]
sum(df_article_communities$title == "Construction of Circumplex Scales for the Inventory of Interpersonal Problems")
V(main_component_graph)[V(main_component_graph)$title == "Construction of Circumplex Scales for the Inventory of Interpersonal Problems"]
```

An article not present in the journal_graph would look like this:

```{r}
V(journal_graph)[V(journal_graph)$node_type == "article" & V(journal_graph)$title == "tHis aRtiCLe doEs NoT ExISt"]
```

Quite a few articles are missing. These articles are present in journal_graph - but not in these communities.

```{r}
sum(df_article_communities$title == "Construction of Circumplex Scales for the Inventory of Interpersonal Problems")
sum(df_article_communities$title == "Personality trait structure as a human universal")
sum(df_article_communities$title == "Evaluating Stability and Change in Personality and Depression")
sum(df_article_communities$title == "On the accuracy of personality judgment: A realistic approach")
sum(df_article_communities$title == "The divided self: Concurrent and longitudinal effects of psychological adjustment and social roles on self-concept differentiation")
```

## Debugging

Which attributes are available in the journal graph?

```{r}
vertex_attr_names(journal_graph)
```


```{r}
vertex_attr_names(co_authorship_graph)
```

```{r}
vertex_attr_names(main_component_graph)
```
