---
title: "Debug Article Titles"
author: "Ian and Chris"
date: "02/23/2022"
output:
  html_document:
    toc: yes
    toc_depth: 5
  pdf_document:
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_depth: 5
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir="../products") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)

library(tm)
library(stm)

source("../R/utils/coauthorship-graph-helper-functions.R")
```

## Introduction

Chris identified some articles that needed to appear in our 1990s Author+Article+Community graph in order for it to be considered valid.
This document represents Ian's work to track down the articles - and this was successful.

The ultimate purpose of this work is to ensure that our topic modelling can proceed with a sufficient number of titles per community.
Having tracked down the missing articles, I think this is now possible.

## Setting up the graphs

### Journal Graph

The Journal Graph consists of all the articles published in journals in the 1990s, along with the authors who published those articles.
The authors are connected to the journals via "authorship" edges.
The authors alre also connected to one-another via "coauthorship" edges.

Here we load the graph and display some summary/diagnostic information about it.

```{r load_journal_graph}
journal_graph = read.graph("../data/graphs/journals-1990s.graphml", format = "graphml")
journal_graph
```

We can visualize the Journal Graph to see that we have loaded something that looks like the network we expected.
There are lots of nodes, they have the names of authors and articles, and there are connections among them.

```{r plot_journal_graph}
plot(journal_graph, layout=layout_with_lgl, vertex.size=1, vertex.label.cex=0.2)
```

### Coauthorship Graph

We obtain the induced subgraph of all authors (i.e. we remove articles, kept authors) in order to preserve only the edges among authors (i.e. co-authorship edges).

```{r load_coauthorship_graph}
# filter by node_type, keep "author"
graph_all_authors = V(journal_graph)[V(journal_graph)$node_type == "author"]
co_authorship_graph = induced.subgraph(graph=journal_graph, vids=graph_all_authors)
co_authorship_graph
```

```{r plot_coauthorship_graph}
plot(co_authorship_graph, layout=layout_with_lgl, vertex.size=1, vertex.label.cex=0.2)
```

### Main Component of Graph

The main component graph contains all of the authors who have some collaboration link among them.

```{r load_main_component_graph}
main_component_graph = get_main_component(journal_graph)
main_component_graph
```

```{r plot_main_component_graph}
plot(main_component_graph, layout=layout_with_lgl, vertex.size=1, vertex.label.cex=0.2)
```

We can inspect these graphs to verify that certain authors are present:

```{r test_find_author}
find_author(journal_graph, "Pennebaker, James W.")
find_author(co_authorship_graph, "Pennebaker, James W.")
find_author(main_component_graph, "Pennebaker, James W.")
```

### Article Communities

```{r get_article_communities}
df_article_communities = get.data.frame(main_component_graph, what="vertices")
df_article_communities = df_article_communities[df_article_communities$node_type=="article",]
df_article_communities = df_article_communities[c("doi", "title", "issn", "abstract", "membership")]
df_article_communities$title = tolower(df_article_communities$title)

head(df_article_communities, n=1)
nrow(df_article_communities)
```

## Testing for presence of expected articles

### Finding an article we expected

The article **Stereotype threat effects on black and white athletic performance** does appear in the communities DF, demonstrating that the code works.

```{r check_article_communities_1}
sum(df_article_communities$title == "linguistic styles: language use as an individual difference")
```

The article is in the journal_graph too.

```{r check_journal_graph_1}
V(journal_graph)[V(journal_graph)$title == "Linguistic styles: Language use as an individual difference"]
```

### One articles that does not appear in DF

An article not present in the journal_graph looks like this:

```{r check_journal_graph_not_found}
V(journal_graph)[V(journal_graph)$node_type == "article" & V(journal_graph)$title == "tHis aRtiCLe doEs NoT ExISt"]
```

The article **Construction of Circumplex Scales for the Inventory of Interpersonal Problems** is present in the journal_graph.

```{r check_journal_graph_2}
V(journal_graph)[V(journal_graph)$node_type == "article" & V(journal_graph)$title == "Construction of Circumplex Scales for the Inventory of Interpersonal Problems"]
```

We can look at the communities df.  It is now there.

```{r check_article_communities_2}
sum(df_article_communities$title == "construction of circumplex scales for the inventory of interpersonal problems")
```

### Other articles that are expected in the data frame

Quite a few articles were missing.  These are all now in the data frame.

```{r others_not_found}
sum(df_article_communities$title == "construction of circumplex scales for the inventory of interpersonal problems")
sum(df_article_communities$title == "personality trait structure as a human universal")
sum(df_article_communities$title == "evaluating stability and change in personality and depression")
sum(df_article_communities$title == "on the accuracy of personality judgment: a realistic approach")
sum(df_article_communities$title == "the divided self: concurrent and longitudinal effects of psychological adjustment and social roles on self-concept differentiation")
```
