---
title: "Article Title Topic Modelling"
author: "Chris, Ian, and Mark"
date: "4/17/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tm)
library(stm)
library(igraph)
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_data, include=FALSE}
# Load Journal and Coauthorship Graphs
co_authorship_1990 = read.graph("../data/graphs/coauthors-merged-journals-1990s.GRAPHML", format = "graphml")
journal_1990 = read.graph("../data/graphs/journals-1990s.GRAPHML", format = "graphml")
```

Inspect number of vertices and edges in `journal_1990`

```{r}
# edges
gsize(journal_1990)

# vertices
gorder(journal_1990)
```

Inspect number of vertices and edges in `co_authorship_1990`

```{r}
# edges
gsize(co_authorship_1990)

# vertices
gorder(co_authorship_1990)
```

```{r examples, include=F}
# Some useful graph operation examples

# print the title of the article represented by vertex_idx
vertex_idx = 1
V(journal_1990)[vertex_idx]$title

# print the name of the author represented by vertex #2 ("Seta, John J.")
V(journal_1990)[2]$author_name

# find an author node ID
author_idx = match("Costa, Paul T.", V(journal_1990)$author_name)

# obtain author vertices
V(journal_1990)[V(journal_1990)$node_type == "author"]

# obtain article vertices
V(journal_1990)[V(journal_1990)$node_type == "article"]

# obtain author by index
V(journal_1990)[author_idx]

# obtain author relationships
relationships = E(journal_1990)[ from(author_idx) ]

# obtain all article relationships from an author
relationships[relationships$edge_type == "authored"]

# obtain all article vertices by an author
V(journal_1990)[relationships[relationships$edge_type == "authored"]]$title

# obtain all edges from graph as data frame
edges_data_frame = get.data.frame(journal_1990, what="edges")

# obtain all vertices from graph as data frame
vertices_data_frame = get.data.frame(journal_1990, what="vertices")

# data frame with all authors and articles
authors = vertices_data_frame[which(vertices_data_frame$node_type == "author"),]
articles = vertices_data_frame[which(vertices_data_frame$node_type == "article"),]
```

## Vertex attributes

Upon examining both graphs, we see they have the same columns as each other.

```{r}
list.vertex.attributes(journal_1990)
```

```{r}
list.vertex.attributes(co_authorship_1990)
```

We can also see that these columns represent a blend of the data schemas for both authors and articles.
There are columns for `title` and `issn`, which apply only to an article, but also columns for `author_name` and `scopus_id` which are applied to authors.
This blended, multi-partite (heterogeneous) graph structure can be queried by filtering on the `node_type` attribute.

```{r}
article_vertices = V(journal_1990)[V(journal_1990)$node_type == "article"]
```

We can also create data frames to represent each object type (authors and articles) independently.

```{r}
# obtain all vertices from graph as data frame
vertices_data_frame = get.data.frame(journal_1990, what="vertices")

# data frame with all authors and articles
authors = vertices_data_frame[which(vertices_data_frame$node_type == "author"),]
authors = authors[c('id', 'author_name', 'scopus_id')]

articles = vertices_data_frame[which(vertices_data_frame$node_type == "article"),]
articles = articles[c('id', 'doi', 'issn', 'journal', 'keywords', 'title', 'abstract', 'cover_date')]
```

## Extract Main Component

We will examine the coauthorship graph (`co_authorship_1990`), which consists of authors but not articles.
This step creates a homogenous, as opposed to multi-partite, graph in which all nodes are of a single type (author).
Correspondingly, all edges between nodes will now be restricted to author-author relationships, including co-authorship.
The clustering operation is therefore applied to only authors and coauthorship edges, resulting in communities based strictly upon coauthorship relationships among authors.

The coauthorship graph is the result of pre-processing the journal graph to first build authorship edges, in which author nodes are connected to the article nodes they authored.
The journal graph was then processed to identify co-authorship by creating new edges between authors who were connected to the same article through authorship.
The final coauthorship graph was then extracted from the multi-partite graph by removing all articles and exporting the resulting graph of authors and coauthorships.

```{r}
# identify clusters in coauthorship graph
coauthorship_components = igraph::clusters(co_authorship_1990, mode="weak")

# the main component is identified by cluster ID with the maximum cluster size
biggest_component_id = which.max(coauthorship_components$csize)

# obtain vertex IDs for members of this largest cluster
component_membership = V(co_authorship_1990)[coauthorship_components$membership == biggest_component_id]

# obtain subgraph consisting of only the members of the main component
main_component_graph = igraph::induced_subgraph(co_authorship_1990, component_membership)
```

## Cluster authors in main component to identify communities

We first obtain communities object using Newman and Girvan's 2004 betweenness clustering approach.
Next, we inspect the community merge structure created during clustering, which is represented as a dendrogram tree with depth proportional to number of communities.
To obtain memberships for 10 communities, we cut the dendrogram at a depth of 10.
Authors are therefore assigned to communities based on the memberships as was merged at this depth in the dendrogram.

```{r author_communities}
# obtain communities object using Newman and Girvan's 2004 betweenness clustering approach
coauthorship_communities = cluster_edge_betweenness(main_component_graph)

# ensure cluster algorithm returns something suitable for passing to communities()
class(coauthorship_communities)

# double-check that communities are hierarchically nested
is_hierarchical(coauthorship_communities)

# cut dendrogram at a specific number of merges to obtain desired number of communities
community_dendrogram = as.dendrogram(coauthorship_communities)
ten_communities = cut_at(coauthorship_communities, 10)

# assign main component author membership according to our 10 communities
V(main_component_graph)$membership = ten_communities

# store resulting authors as a data frame
tmp_data_frame = get.data.frame(main_component_graph, what="vertices")
df_authors = tmp_data_frame[which(tmp_data_frame$node_type == "author"),]
df_authors = df_authors[c('id', 'author_name', 'scopus_id', 'membership')]
head(df_authors)
```

## Identify articles authored by members of Main Component

Now that we have identified which authors belong to which communities, we return to the multi-partite graph (`journal_1990`) in order to connect authors with articles.
We wish to identify those articles that were published by authors in the main component.

```{r}
df_article_communities = data.frame(
  id=character(),
  title=character(),
  community=integer()
)

for (scopus_id_str in df_authors$scopus_id) {
  # obtain an author vertex based on Scopus ID
  author_in_articles_vertex = V(journal_1990)[which(V(journal_1990)$scopus_id == scopus_id_str )]
  author_in_component_vertex = V(main_component_graph)[which(V(main_component_graph)$scopus_id == scopus_id_str )]
  author_membership = author_in_component_vertex$membership
  
  # identify all edges emanating from this author
  author_relationships = E(journal_1990)[ from(author_in_articles_vertex) ]

  # filter edges to identify authorship edges only
  authorship_edges = author_relationships[author_relationships$edge_type == "authored"]

  # iterate article edges to individually add article IDs to list
  for (article_edge in authorship_edges) {
    if (article_edge < gorder(journal_1990)) {
      article = V(journal_1990)[article_edge]

      if (article$title != "None") {
        df_tmp = data.frame(id=as.character(article$id), title=article$title, community=author_membership)
        df_article_communities = rbind(df_article_communities, df_tmp)
      }

    }
  }
}

head(df_article_communities)
```

Once the articles have been identified, they may be labeled according to the communities their authors belong to.
